Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-07 doc/JFLA2022/paper.tex
add references to two chapters of the book

Unfortunately, the examples  most commonly shown in the litterature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.
We prove now that Theorem~\ref{thm3} still holds with these typical battles by borrowing new combinatorial results from~\cite{KS81}.
Since we are looking  for a minoration of the length of such battles,
we can work with the following hypotheses and invariants, 
without any loss of generality.

@@

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from~\cite{KS81}.

@@

Computability is a key topic in Computer Science teaching. Moreover O'Connor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter to this formalization, with comments on the definitions and proofs, [counter]-examples and exercises, and  extract part of the Goedel library into a new sub-library of the \Hydras library: Ackermann.

>>>>

Unfortunately, the examples  most commonly shown in the litterature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $n$ copies at step $n$ of the game, which is incompatible with our proof.
We prove now that Theorem~\ref{thm3} still holds with these typical battles.
%by borrowing new combinatorial results from~\cite{KS81}.
Since we are looking  for a minoration of the length of such battles,
we can work with the following hypotheses and invariants, 
without any loss of generality.

@@

 Our new proof of Theorem~\ref{thm3} is based on a systematic study of strictly decreasing sequences of ordinals below $\epsilon_0$, borrowed from Ketonen and Solovay~\cite{KS81}, and the formalization of which is described  in chapter 5 of~\cite{HydraBook}.

@@

Computability is a key topic in Computer Science teaching. Moreover O'Connor's library is a nice illustration of dependently typed programming, so we chose to devote a full chapter (chapter 9 of~\cite{HydraBook}) to this formalization, with comments on the definitions and proofs, [counter]-examples and exercises, and  extract part of the Goedel library into a new sub-library of the \Hydras library: Ackermann.
